Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
polished appendix

\begin{document}
\begin{abstract}
\noindent
The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped 
with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as 
inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \maps 
\A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
$\mathbb{X}$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
networks which goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to 
`decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure. Using a slight variation of 
Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax 
monoidal pseudofunctor using a well known construction of Grothendieck.
\end{abstract}

@@

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]

We call $A, B, C$ and $D$ \textbf{objects} or \textbf{0-cells}, $f$ and $g$ \textbf{vertical 1-morphisms}, $M$ and $N$ \textbf{horizontal 1-cells} and $a$ a \textbf{2-morphism}. Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'. We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

\begin{defn}\label{defn:double_category}
A \textbf{pseudo double category} $\lD$, or $\textbf{double category}$ for short, consists of a category of objects $\mathbf{D_{0}}$ and a category of arrows $\mathbf{D_1}$ with the following functors
\begin{center}
$U\maps \mathbf{D_{0}} \to \mathbf{D_1}$\\
$S,T \maps \mathbf{D_1} \rightrightarrows \mathbf{D_{0}}$\\
$\odot \maps \mathbf{D_1} \times_{\mathbf{D_{0}}} \mathbf{D_1} \to \mathbf{D_1}$ (where the pullback is taken over $\mathbf{D_1} \xrightarrow[]{T} \mathbf{D_{0}} \xleftarrow[]{S} \mathbf{D_1}$) \\
\end{center}
 such that \\
\begin{center}
$S(U_{A})=A=T(U_{A})$\\
$S(M \odot N)=SN$\\
$T(M \odot N)=TM$\\
\end{center}
equipped with natural isomorphisms
\begin{center}

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\mathbf{D_{0}}$ are called $\textbf{0-cells}$ and morphisms of $\mathbf{D_{0}}$ are called $\textbf{vertical 1-morphisms}$. Objects of $\mathbf{D_1}$ are called $\textbf{horizontal 1-cells}$ and morphisms of $\mathbf{D_1}$ are called $\textbf{2-morphisms}$. The morphisms of $\mathbf{D_{0}}$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\mathbf{D_1}$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}

The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism. Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$. We will sometimes omit the word pseudo and simply say double category.

\begin{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.
\end{defn}

\begin{defn}
Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
\end{defn}

\begin{defn}\label{def:doublefun}
Let $\mathbb{A}$ and $\mathbb{B}$ be pseudo double categories. A \define{lax double functor} is a functor $\mathbb{F} \maps\mathbb{A}\to \mathbb{B}$ that takes items of $\mathbb{A}$ to items of $\mathbb{B}$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$. This means that we have functors $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{B}_0$ and $\mathbb{F}_1 \maps \mathbb{A}_1 \to \mathbb{B}_1$ such that the following equations are satisfied: $$S \circ \mathbb{F}_1 = \mathbb{F}_0 \circ S$$ $$T \circ \mathbb{F}_1 = \mathbb{F}_0 \circ T$$ Sometimes for brevity, we will omit the subscripts and simply say $\mathbb{F}$. As to whether we mean $\mathbb{F}_0$ or $\mathbb{F}_1$ will be clear from context.

Also, every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\mathbb{F}(a)} \to \mathbb{F}(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \mathbb{F}(N_1) \odot \mathbb{F}(N_{2}) \to \mathbb{F}(N_1 \odot N_{2})$ (the composition comparison), in a coherent way. This means that the following diagrams commute.

@@

\begin{equation}\label{eq:square}
  \xymatrix@-.5pc{
    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})}  \ar[d] \ar@{}[dr]|{\mathbb{F}(\alpha)}&
    \mathbb{F}(B) \ar[d] \ar[r]|{|}^{\mathbb{F}(N_1)} \ar@{}[dr]|{\mathbb{F}(\beta)}&
    \mathbb{F}(C) \ar[d] &
     &
    \mathbb{F}(A) \ar[r]|{|}^{\mathbb{F}(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
    \mathbb{F}(B) \ar[r]|{|}^{\mathbb{F}(N_1)} &
    \mathbb{F}(C) \ar[d]^{1} \\
    \mathbb{F}(A') \ar[r]|{|}_{\mathbb{F}(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
    \mathbb{F}(B') \ar[r]|{|}_{\mathbb{F}(N_{3})} &
    \mathbb{F}(C') \ar[d]^{1}&
    = &
    \mathbb{F}(A) \ar[rr]|{|}^{\mathbb{F}(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\mathbb{F}(\beta \odot \alpha)}&
     &
    \mathbb{F}(C) \ar[d] \\
    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} & 
     & 
    \mathbb{F}(C') &
     &
    \mathbb{F}(A') \ar[rr]|{|}_{\mathbb{F}(N_{3} \odot N_{4})} &
     &
    \mathbb{F}(C') \\
  }.
\end{equation}

@@

\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$\mathbb{F}(N) \odot 1_{\mathbb{F}(A)}$};
\node (C) at (3,1) {$\mathbb{F}(N)$};
\node (A') at (1,-1) {$\mathbb{F}(N) \odot \mathbb{F}(1_{A})$};
\node (C') at (3,-1) {$\mathbb{F}(N \odot 1_{A})$};
\node (B) at (5,1) {$1_{\mathbb{F}(B)} \odot \mathbb{F}(N)$};
\node (B') at (5,-1) {$\mathbb{F}(1_{B}) \odot \mathbb{F}(N)$};
\node (D) at (7,1) {$\mathbb{F}(N)$};
\node (D') at (7,-1) {$\mathbb{F}(1_{B} \odot N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1 \odot \phi_{A}$} (A')
(C') edge node[right]{$\mathbb{F} \rho$} (C)
(A) edge node[above]{$\rho_{\mathbb{F}(N)}$} (C)
(A') edge node[above]{$\phi(N,1_{A})$} (C')
(B) edge node[left]{$\phi_{B} \odot 1$} (B')
(B') edge node[above]{$\phi(1_{B},N)$} (D')
(B) edge node[above]{$\lambda_{\mathbb{F}(N)}$} (D)
(D') edge node[right]{$F \lambda$} (D);
\end{tikzpicture}
\]

@@

 \[\xymatrix{
    (\mathbb{F}(N_1) \odot \mathbb{F}(N_{2})) \odot \mathbb{F}(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
    & \mathbb{F}(N_1) \odot (\mathbb{F}(N_{2}) \odot \mathbb{F}(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
    \mathbb{F}(N_1 \odot N_{2}) \odot \mathbb{F}(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
    \mathbb{F}(N_1) \odot \mathbb{F}(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
    \mathbb{F}((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\mathbb{F}a} &
    \mathbb{F}(N_1 \odot (N_{2} \odot N_{3}))}\]
\end{enumerate}
We say the double functor $\mathbb{F}$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
\end{defn}

%!!! Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
\begin{defn}
A double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\mathbb{F}_{M,N} \maps \mathbb{F}(M) \odot \mathbb{F}(N) \xrightarrow{\sim} \mathbb{F}(M \odot N)$$and for each object $a \in \mathbb{A}$ a natural isomorphism $$\mathbb{F}_a \maps \hat{U}_{\mathbb{F}(a)} \xrightarrow{\sim} \mathbb{F}(U_a).$$
\end{defn}

Following the notation of Shulman \cite{Shulman2010}, given a double category $\mathbb{A}$, we write $_f \mathbb{A}_g(M,N)$ for the set of 2-morphisms in $\mathbb{A}$ of the form:
\[
  \xymatrix@-.5pc{
    A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
    B\ar[d]^g\\
    C \ar[r]|{|}_N & D
  }
\]
We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \mathbb{A}_g(M,N)$ denotes the set of 2-morphisms in $\mathbb{A}$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.
\begin{defn}\label{def:fullfaithful}
A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{full} (respectively, \define{faithful}) if $\mathbb{F}_0 \maps \mathbb{A}_0 \to \mathbb{X}_0$ is full (respectively, faithful) and each map $$\mathbb{F}_1 \maps _f \mathbb{A}_g(M,N) \to _{\mathbb{F}(f)} \mathbb{X}_{\mathbb{F}(g)}(\mathbb{F}(M),\mathbb{F}(N))$$ is surjective (respectively, injective).
\end{defn}
\begin{defn}\label{def:essentiallysurj}
A (possibly lax or oplax) double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is \define{essentially surjective} if we can simultaneously make the following choices:
\begin{enumerate}
\item{For each object $x \in \mathbb{X}$, we can find an object $a \in \mathbb{A}$ together with a vertical 1-isomorphism $\alpha_x \maps \mathbb{F}(a) \to x$, and}
\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\mathbb{X}$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\mathbb{A}$ and a 2-isomorphism $a_{N}$ of $\mathbb{X}$ as in the following diagram:
\[
  \xymatrix@-.5pc{
    \mathbb{F}(a_1) \ar[r]|{|}^{\mathbb{F}(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
    \mathbb{F}(a_1) \ar[d]^{\alpha_{x_2}}\\
    x_1 \ar[r]|{|}_N & x_2
  }
\]
}
\end{enumerate}
\end{defn}

Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
Similarly to ordinary equivalence of categories, [Shulman,7.8] allows us to use the following equivalent characterization.

\begin{thm}\label{ShulDubEquiv}
A strong double functor $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
\end{thm}

\begin{prop}
Let $\mathbb{A}$ and $\mathbb{X}$ be symmetric monoidal double categories and let $\mathbb{F} \maps \mathbb{A} \to \mathbb{X}$ be a symmetric monoidal strong double functor. If $\mathbb{F}$ is part of a double equivalence, then $\mathbb{F}$ is in fact part of a symmetric monoidal double equivalence, and $\mathbb{A}$ and $\mathbb{X}$ are equivalent as symmetric monoidal double categories.
\end{prop}

@@

		\item $\lD_{0}$ and $\lD_1$ are braided monoidal categories.

@@

		\item $\lD_{0}$ and $\lD_1$ are symmetric monoidal.

@@

\begin{defn}
\label{defn:fibrant}
We say that a double category is \textbf{fibrant} if every vertical
1-morphism has both a companion and a conjoint and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
\end{defn}

\begin{defn}
\label{defn:monoidal_double_functor}
A \define{(strong) monoidal lax double functor} $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a lax double functor $\mathbb{F} \maps \mathbb{C} \to \mathbb{D}$ such that
	\begin{itemize}
		\item $\mathbb{F}_0$ and $\mathbb{F}_1$ are monoidal functors, meaning that there exists

>>>>

\begin{document}
\begin{abstract}
\noindent
The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped 
with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as 
inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \maps 
\A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
$\lX$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
networks which goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to 
`decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure. Using a slight variation of 
Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax 
monoidal pseudofunctor using a well known construction of Grothendieck.
\end{abstract}

@@

\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
We call $A, B, C$ and $D$ \define{objects} or \define{0-cells}, $f$ and $g$ \define{vertical 1-morphisms}, $M$ and $N$ \define{horizontal 1-cells} and $a$ a \define{2-morphism}. Note that a vertical 1-morphism is a morphism between 0-cells and a 2-morphism is a morphism between horizontal 1-cells. %We will denote both kinds of morphisms and horizontal 1-cells as a single arrow, namely `$\to$'???   Or should we put a ``tick'' in here?
We follow the notation of Shulman \cite{Shulman2008} with the following definitions.

\begin{defn}\label{defn:double_category}
A \textbf{(pseudo) double category} $\lD$ consists of a category of objects $\lD_0$ and a category of arrows $\lD_1$ with the following functors
\begin{center}
$U\maps \lD_0 \to \lD_1$\\
$S,T \maps \lD_1 \rightrightarrows \lD_0$\\
$\odot \maps \lD_1 \times_{\lD_0} \lD_1 \to \lD_1$ (where the pullback is taken over $\lD_1 \xrightarrow[]{T} \lD_0 \xleftarrow[]{S} \lD_1$) \\
\end{center}
 such that \\
\begin{center}
$S(U_{A})=A=T(U_{A})$\\
$S(M \odot N)=SN$\\
$T(M \odot N)=TM$\\
\end{center}
equipped with natural isomorphisms
\begin{center}

@@

\end{center}
such that $S(\alpha), S(\lambda), S(\rho), T(\alpha), T(\lambda)$ and $T(\rho)$ are all identities and that the coherence axioms of a monoidal category are satisfied. Following the notation of Shulman, objects of $\lD_0$ are called \define{0-cells} or \define{objects} and morphisms of $\lD_0$ are called \define{vertical 1-morphisms}. Objects of $\lD_1$ are called \define{horizontal 1-cells} and morphisms of $\lD_1$ are called \define{2-morphisms}. The morphisms of $\lD_0$, which are vertical 1-morphisms, will be denoted $f \maps A \to C$ and we denote a 1-cell $M$ with $S(M)=A,T(M)=B$ by $M \maps A \to B$. Then a 2-morphism $a \maps M \to N$ of $\lD_1$ with $S(a)=f,T(a)=g$ would look like:
\[
\begin{tikzpicture}[scale=1]
\node (D) at (-4,0.5) {$A$};
\node (E) at (-2,0.5) {$B$};
\node (F) at (-4,-1) {$C$};
\node (A) at (-2,-1) {$D$};
\node (B) at (-3,-0.25) {$\Downarrow a$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above]{$M$}(E)
(E) edge node [right]{$g$}(A)
(D) edge node [left]{$f$}(F)
(F) edge node [above]{$N$} (A);
\end{tikzpicture}
\]
\end{defn}
A 2-morphism where $f$ and $g$ are identities is called a \textbf{globular 2-morphism}.

%The key difference between a `strict' double category and a pseudo double category is that in a pseudo double category, horizontal composition is associative and unital only up to natural isomorphism. Equivalently, as a double category can be viewed as a category internal to $\Cat$, we can view a pseudo double category as a category `weakly' internal to $\Cat$. We will sometimes omit the word pseudo and simply say double category.

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}

\begin{defn}\label{def:doublefun}
Let $\lA$ and $\lB$ be double categories. A \define{(pseudo) double functor} is a functor $\lF \maps\lA\to \lB$ that takes items of $\lA$ to items of $\lB$ of the corresponding type, respecting vertical composition in the strict sense and the horizontal composition up to an assigned comparison $\phi$. This means that we have functors $\lF_0 \maps \lA_0 \to \lB_0$ and $\lF_1 \maps \lA_1 \to \lB_1$ such that the following equations are satisfied: 
\[   S \circ \lF_1 = \lF_0 \circ S, \qquad  T \circ \lF_1 = \lF_0 \circ T. \]
Sometimes for brevity we omit the subscripts and simply write $\lF$.

Every object $a$ is equipped with a special globular 2-morphism $\phi_{a} \maps 1_{\lF(a)} \to \lF(1_{a})$ (the identity comparison), and every horizontal composition $N_1 \odot N_{2}$ is equipped with a special globular 2-morphism $\phi(N_1,N_{2}) \maps \lF(N_1) \odot \lF(N_{2}) \to \lF(N_1 \odot N_{2})$ (the composition comparison), in a coherent way. This means that the following diagrams commute.

@@

\begin{equation}\label{eq:square}
  \xymatrix@-.5pc{
    \lF(A) \ar[r]|{|}^{\lF(N_{2})}  \ar[d] \ar@{}[dr]|{\lF(\alpha)}&
    \lF(B) \ar[d] \ar[r]|{|}^{\lF(N_1)} \ar@{}[dr]|{\lF(\beta)}&
    \lF(C) \ar[d] &
     &
    \lF(A) \ar[r]|{|}^{\lF(N_{2})} \ar@{}[drr]|{\phi(N_1,N_{2})} \ar[d]_1 &
    \lF(B) \ar[r]|{|}^{\lF(N_1)} &
    \lF(C) \ar[d]^{1} \\
    \lF(A') \ar[r]|{|}_{\lF(N_{4})} \ar@{}[drr]|{\phi(N_{3},N_{4})} \ar[d]_1&
    \lF(B') \ar[r]|{|}_{\lF(N_{3})} &
    \lF(C') \ar[d]^{1}&
    = &
    \lF(A) \ar[rr]|{|}^{\lF(N_1 \odot N_{2})} \ar[d] \ar@{}[drr]|{\lF(\beta \odot \alpha)}&
     &
    \lF(C) \ar[d] \\
    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} & 
     & 
    \lF(C') &
     &
    \lF(A') \ar[rr]|{|}_{\lF(N_{3} \odot N_{4})} &
     &
    \lF(C') \\
  }.
\end{equation}

@@

\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (1,1) {$\lF(N) \odot 1_{\lF(A)}$};
\node (C) at (3,1) {$\lF(N)$};
\node (A') at (1,-1) {$\lF(N) \odot \lF(1_{A})$};
\node (C') at (3,-1) {$\lF(N \odot 1_{A})$};
\node (B) at (5,1) {$1_{\lF(B)} \odot \lF(N)$};
\node (B') at (5,-1) {$\lF(1_{B}) \odot \lF(N)$};
\node (D) at (7,1) {$\lF(N)$};
\node (D') at (7,-1) {$\lF(1_{B} \odot N)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1 \odot \phi_{A}$} (A')
(C') edge node[right]{$\lF \rho$} (C)
(A) edge node[above]{$\rho_{\lF(N)}$} (C)
(A') edge node[above]{$\phi(N,1_{A})$} (C')
(B) edge node[left]{$\phi_{B} \odot 1$} (B')
(B') edge node[above]{$\phi(1_{B},N)$} (D')
(B) edge node[above]{$\lambda_{\lF(N)}$} (D)
(D') edge node[right]{$F \lambda$} (D);
\end{tikzpicture}
\]

@@

 \[\xymatrix{
    (\lF(N_1) \odot \lF(N_{2})) \odot \lF(N_{3}) \ar[r]^{a'}\ar[d]_{\phi(N_1,N_{2}) \odot 1}
    & \lF(N_1) \odot (\lF(N_{2}) \odot \lF(N_{3})) \ar[d]^{1 \odot \phi(N_{2},N_{3})}\\
    \lF(N_1 \odot N_{2}) \odot \lF(N_{3}) \ar[d]_{\phi(N_1 \odot N_{2},N_{3})} &
    \lF(N_1) \odot \lF(N_{2} \odot N_{3}) \ar[d]^{\phi(N_1,N_{2} \odot N_{3})}\\
    \lF((N_1 \odot N_{2}) \odot N_{3})\ar[r]^{\lF(a)} &
    \lF(N_1 \odot (N_{2} \odot N_{3}))}\]
\end{enumerate}
We say the double functor $\lF$ is \define{strict} if the comparison constraints $\phi_a$ and $\phi_{N_1,N_2}$ are identities, \define{pseudo} if the comparison constraints are isomorphisms, and \define{oplax} if the comparison constraints go in the opposite direction.
\end{defn}

%!!! Christina: Pretty sure the def below can be incorporated above, however got a bit lost in different notation. Kenny Fix?
%\begin{defn}
%A double functor $\lF \maps \lA \to \lX$ is \define{strong} if the comparison and unit constraints are globular isomorphisms, meaning that for each composable pair of horizontal 1-cells $M$ and $N$ we have a natural isomorphism $$\lF_{M,N} \maps \lF(M) \odot \lF(N) \xrightarrow{\sim} \lF(M \odot N)$$and for each object $a \in \lA$ a natural isomorphism $$\lF_a \maps \hat{U}_{\lF(a)} \xrightarrow{\sim} \lF(U_a).$$
%\end{defn}

%Following the notation of Shulman \cite{Shulman2010}, given a double category $\lA$, we write $_f \lA_g(M,N)$ for the set of 2-morphisms in $\lA$ of the form:
%\[
% \xymatrix@-.5pc{
%   A \ar[r]|{|}^{M}  \ar[d]_f \ar@{}[dr]|{\Downarrow a}&
%    B\ar[d]^g\\
%    C \ar[r]|{|}_N & D
%  }
%\]
We call $M$ and $N$ the \define{horizontal source and target} of the 2-morphism $a$, respectively, and likewise we call $f$ and $g$ the \define{vertical source and target} of the 2-morphism $a$, respectively. Thus $_f \lA_g(M,N)$ denotes the set of 2-morphisms in $\lA$ with horizontal source and target $M$ and $N$ and vertical source and target $f$ and $g$.

\begin{defn}\label{def:fullfaithful}
A double functor $\lF \maps \lA \to \lX$ is \define{full} (respectively, \define{faithful}) if $\lF_0 \maps \lA_0 \to \lX_0$ is full (respectively, faithful) and each map $$\lF_1 \maps _f \lA_g(M,N) \to _{\lF(f)} \lX_{\lF(g)}(\lF(M),\lF(N))$$ is surjective (respectively, injective).
\end{defn}
\begin{defn}\label{def:essentiallysurj}
A double functor $\lF \maps \lA \to \lX$ is \define{essentially surjective} if we can simultaneously make the following choices:
\begin{enumerate}
\item{For each object $x \in \lX$, we can find an object $a \in \lA$ together with a vertical 1-isomorphism $\alpha_x \maps \lF(a) \to x$, and}
\item{For each horizontal 1-cell $N \maps x_1 \tobar x_2$  of $\lX$, we can find a horizontal 1-cell $M \maps a_1 \tobar a_2$ of $\lA$ and a 2-isomorphism $a_{N}$ of $\lX$ as in the following diagram:
\[
  \xymatrix@-.5pc{
    \lF(a_1) \ar[r]|{|}^{\lF(M)}  \ar[d]_{\alpha_{x_1}} \ar@{}[dr]|{\Downarrow a_N}&
    \lF(a_1) \ar[d]^{\alpha_{x_2}}\\
    x_1 \ar[r]|{|}_N & x_2
  }
\]
}
\end{enumerate}
\end{defn}

Formally, two strong double functors between two double categories form a \emph{double equivalence} if ...
% FINISH THIS OR DISCARD IT!!!
%{\chris their two-way composite is isomorphic to the identity, better expressed, possibly in a definition environment}. 
Much like equivalence of categories, equivalence of double categories has an alternative characterization:

\begin{thm}{\cite[Thm.\ 7.8]{Shulman2010}}
\label{ShulDubEquiv}
A strong double functor $\lF \maps \lA \to \lX$ is part of a double equivalence if and only if it is full, faithful and essentially surjective.
\end{thm}

\begin{thm}
Let $\lA$ and $\lX$ be symmetric monoidal double categories and let $\lF \maps \lA \to \lX$ be a symmetric monoidal strong double functor. If $\lF$ is part of a double equivalence, then $\lF$ is in fact part of a symmetric monoidal double equivalence, and $\lA$ and $\lX$ are equivalent as symmetric monoidal double categories.
\end{thm}

\begin{proof} Where is this proved???  \end{proof}

@@

		\item $\lD_0$ and $\lD_1$ are braided monoidal categories.

@@

		\item $\lD_0$ and $\lD_1$ are symmetric monoidal.

@@

\begin{defn}
\label{defn:fibrant}
We say that a double category is \textbf{fibrant} if every vertical
1-morphism has both a companion and a conjoint.  % and \define{isofibrant} if every vertical 1-isomorphism has both a companion and a conjoint.
\end{defn}

\begin{defn}
\label{defn:monoidal_double_functor}
A \define{(strong) monoidal double functor} $\lF \maps \mathbb{C} \to \mathbb{D}$ between monoidal double categories $\mathbb{C}$ and $\mathbb{D}$ is a double functor $\lF \maps \mathbb{C} \to \mathbb{D}$ such that
	\begin{itemize}
		\item $\lF_0$ and $\lF_1$ are monoidal functors, meaning that there exists
